The language of generalization: Probability, vagueness, and interaction

### 2018-02-08 paper/case2-habituals.Rmd
port over more code into scripts

```{r habituals-endorsement-gender-exploration}
load("cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

@@

```{r habituals-regression-models}
load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression

@@

```{r habituals-rsamodels}
load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions

@@

movies.year.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "goes to the movies", time_period == "year"))

@@

banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorsement.bayes, habitual == "plays the banjo", time_period == "2 years"))

banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
                                                        time_period == "2 years"),
                                                        estimate = "prediction",
                                                        low = "prediction_lower",
                                                        high = "prediction_upper")
```

@@

```{r hab-fixed-parameters}
```

```{r hab-fixed-threshold-examples, eval =F}
```

@@

```{r habituals-predictive-elicitation}
d.hab.predictive <- read.csv(paste(
  project.path, "data/habituals/predictive/", "predictive-1-trials.csv", sep = ""))

n.subj.hab.pred <- length(unique(d.hab.predictive$workerid))
ave.seconds.hab.pred <-  d.hab.predictive %>% select(workerid, rt) %>%
      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
      summarize(total = mean(totalSec))

# participant reported this in the comments section (it was recorded as a symbol)
d.hab.predictive[
  (d.hab.predictive$workerid==44 & 
     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))

d.hab.predictive<- d.hab.predictive %>%
  rowwise() %>%
  mutate(
    annualPredictiveRate =
           annualRates[[as.character(past_interval)]]*response,
    annualPastRate =
           annualRates[[as.character(past_interval)]]*past_freq,
    annualPredictiveRate = ifelse(
      annualPredictiveRate == 0, 0.05, 
      annualPredictiveRate),
    logAnnualPredictiveRate = log(annualPredictiveRate),
    logAnnualPastRate = log(annualPastRate)
    )

d.hab.predictive.summary <- d.hab.predictive %>%
  group_by(condition, item, logAnnualPastRate) %>%
  multi_boot_standard(col = "logAnnualPredictiveRate")

r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)

fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency (log scale)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

```{r habituals-predictive-model}
hab.predictive.bda.model <- '
var model = function(){

	var predictiveFrequency = {
			mu: uniformDrift({a: -5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:10, width: 1})
	}

	mapData({data: data}, function(d){
		observe(Gaussian(predictiveFrequency),
        d.logAnnualPredictiveRate)
	})

  return predictiveFrequency
}
'
```

```{r habituals-predictive-model-run, cache = T, eval=F}
items <- levels(factor(d.hab.predictive$item))
conditions <- levels(factor(d.hab.predictive$condition))
n_samples <- 5000
rs.habituals.bda.predictive <- data.frame()

for (it in items){
  for (cn in conditions){
     df.predictive.toPass <- d.hab.predictive %>%
       filter(condition == cn, item == it)

    rs <- webppl(program_code = hab.predictive.bda.model,
       model_var = "model",
       inference_opts = list(method = "MCMC", samples = n_samples,
                             burn = n_samples / 2),
       data = df.predictive.toPass,
       data_var = "data")
    rs.habituals.bda.predictive <- bind_rows(
        rs.habituals.bda.predictive, 
        rs %>% 
            mutate(item = it, condition = cn) 
        )
  }
}
```

```{r eval = F}
  d.hab.predictive %>% 
    mutate(src = 'data') %>% 
    select(item, condition, src, logAnnualPredictiveRate) %>%
ggplot(. , aes( x = logAnnualPredictiveRate, fill = condition))+
#  geom_density(size = 1, aes( y = ..scaled.. ))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
               position = position_dodge())+
  facet_wrap(~item, scales = 'free')+
  scale_color_solarized()+
  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_x_continuous(limits = c(-5,10)) +
  theme(strip.text.y = element_text(angle = 0))
```

```{r habituals-predictive-bda-forwardSample, fig.width=14, eval=F}
rs.habituals.bda.predictive.samples <- rs.habituals.bda.predictive %>% 
  spread(Parameter, value) %>%
  rowwise() %>%
  mutate(
    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
  )

  d.hab.predictive %>% 
    mutate(src = 'data') %>% 
    select(item, condition, src, logAnnualPredictiveRate) %>%
ggplot(. , aes( x = logAnnualPredictiveRate, color = condition))+
#  geom_density(size = 1, aes( y = ..scaled.. ))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
               position = position_dodge())+
  facet_wrap(~item, scales = 'free')+
  scale_color_solarized()+
  #scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_x_continuous(limits = c(-5,10)) +
  theme(strip.text.y = element_text(angle = 0))

bind_rows(
  d.hab.predictive %>% 
    mutate(src = 'data') %>% 
    select(item, condition, src, logAnnualPredictiveRate),
  rs.habituals.bda.predictive.samples %>% 
    select(item, condition, logannualRate) %>%
    rename(logAnnualPredictiveRate = logannualRate) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(. , aes( x = logAnnualPredictiveRate, color = src))+
  geom_density(size = 1, aes( y = ..scaled.. ))+
#  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
#               position = position_dodge())+
  facet_grid(condition ~ item )+
  scale_color_solarized()+
  scale_x_continuous(limits = c(-5,10)) +
  #scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

```{r habituals-predictive-bda-summary, eval =F}
rs.habituals.bda.predictive.summary <- rs.habituals.bda.predictive %>% 
  spread(Parameter, value) %>%
  rowwise() %>%
  mutate(
    logannualRate = rnorm(n = 1, mean = mu, sd = sigma)
  ) %>%
  gather(key, val, mu, sigma, logannualRate) %>%
  group_by(item, condition, key) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```

```{r habituals-predictive-bda-figure, eval =F}
fig.hab.freq.predictive.vs.past <- left_join(
  rs.habituals.bda.predictive.summary %>% filter(key == "logannualRate"),
  unique(d.hab.predictive %>% 
    select(item, condition, logAnnualPastRate)
  )) %>% ggplot(., 
       aes(x=logAnnualPastRate, y = MAP, 
                              ymin = cred_lower, ymax = cred_upper, 
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6)+
  scale_shape_manual(values=c(21,22,23, size = 4))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-4,7), 
                     breaks = c(-4, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency MAP (log scale)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r habituals-predictive-endorsement}
d.hab.predictive.endorsment <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
d.hab.predictive.endorsment.catch <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))

n.subj.hab.pred.endorse <- length(unique(d.hab.predictive.endorsment$workerid))
ave.seconds.hab.pred.endorse <-  d.hab.predictive.endorsment %>% select(workerid, rt) %>%
      group_by(workerid) %>% summarize(totalSec= sum(rt) / 1000) %>% ungroup() %>% 
      summarize(total = mean(totalSec))

d.hab.predictive.endorsment.condition.summary <- left_join(
  d.hab.predictive.endorsment, 
  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
  by = "workerid"
  ) %>% filter(pass==1) %>%
  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
  rename(item = habitual) %>%
  group_by(condition) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

@@

d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
  filter(condition == 'enabling')

d.hab.predictive.endorsment.summary <- left_join(
  d.hab.predictive.endorsment, 
  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
  by = "workerid"
  ) %>% filter(pass==1) %>%
  mutate(response = ifelse(response=="agree-key", 1, 0),
         time_period = factor(time_period,
                              levels=c("month",
                                       "2 months",
                                       "year",
                                       "2 years",
                                       "5 years")),
         condition = factor(condition,
                            levels=c("enabling", "baseline", "preventative")),
         hab_time = paste(habitual, time_period, sep='-')) %>%
  rename(item = habitual) %>%
  group_by(item, condition, hab_time, time_period) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

d.hab.predictive.endorsment.summary <- left_join(
  d.hab.predictive.endorsment.summary,
  d.hab.predictive.summary %>%
    rename(logAnnualFutureRate = mean,
         future_lower = ci_lower, future_upper = ci_upper)
  # rs.habituals.bda.predictive.summary %>% 
  #   filter(key == "logannualRate") %>%
  #   rename(logAnnualFutureRate = MAP,
  #        future_lower = cred_lower, future_upper = cred_upper)
  # %>%
  #   rowwise() %>%
  #   mutate(future_lower = ifelse(future_lower < -4, -4, future_lower),
  #          future_upper = ifelse(future_upper > 7, 7, future_upper))
)

@@

```{r habituals-predictive-rsa}
n_chains <- 3
# n_samples <- 500000
# burn <- n_samples / 2
# lg <- 150
model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
n_samples <- 100000
burn <- n_samples / 2
lg <- 50

@@

```{r fig.height = 6, fig.width=14, echo = F, eval=F}
m.hab.pred.samp %>%
  filter(type == "predictive", C == "predictiveFreq", E == "sigma") %>%
  #filter(type == "predictive", C == "endorsement") %>%
#  mutate(E = as.numeric(as.character(E))) %>%
  ggplot(., aes(x = val, fill = D))+
  geom_histogram(position = position_dodge())+
  #facet_grid(B~E)+
  facet_grid(D~B)
```

```{r, eval = F}
m.hab.predfreq.summary <- m.hab.pred.samp %>%
  filter(type == "predictive", C == "predictiveFreq") %>%
  group_by(B, D, E) %>%
  summarize(MAP = estimate_mode(val)) %>% spread(E, MAP)

left_join(m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Endorsement model (past frequency)",
                                 "Endorsement model (predictive frequency)"

                                 ))) %>%
  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
```

@@

Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r r.hab.pred.past.baseline.freq`$). 
That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
This result implies that our model makes identical predictions for Expt. 2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).

```{r habituals-predictive-elicitation-predictions}
lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
       (1 + condition | workerid) + 
       (1 + condition | item)
)
lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
```

>>>>

```{r habituals-endorsement-gender-exploration}
load("cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression
load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, md.hab, hab.listener.predictions

gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

@@

```{r habituals-regression-models}

@@

```{r habituals-rsamodels}

@@

movies.year.data <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "goes to the movies", time_period == "year"))

@@

banjo.2years.data <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo", time_period == "2 years"))

banjo.2years.regression.distinct <- format_endorsment_ci(filter(d.hab.endorse.regression.freq.mix, habitual == "plays the banjo",
                                                        time_period == "2 years"),
                                                        estimate = "prediction",
                                                        low = "prediction_lower",
                                                        high = "prediction_upper")

@@

@@

```{r}
load("cached_results/case2_predictive_data.RData")
#d.hab.predictive.endorsment.summary, d.hab.predictive.summary, n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse,n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, lmer.rs.hab.predictive.summary
```

```{r, cache = F}
r.hab.pred.past.baseline.freq <- round(with(d.hab.predictive.summary %>% filter(condition == "baseline"), cor(logAnnualPastRate, mean)), 3)
n.hab.pred.past.baseline.freq <- length(filter(d.hab.predictive.summary, condition == "baseline")$mean)

@@

d.hab.predictive.endorsment.enabling.summary <- d.hab.predictive.endorsment.condition.summary %>%
  filter(condition == 'enabling')
```

```{r fighabfreq_predictive_vs_past, cache = F}
fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency (log scale)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r habituals-predictive-endorsement, cache = F}

@@

fig.hab.endorse.vs.predfreq
```

```{r habituals-predictive-rsa, cache = F}
n_chains <- 3
# n_samples <- 500000
# burn <- n_samples / 2
# lg <- 150
model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
n_samples <- 100000
burn <- n_samples / 2
lg <- 50

@@

@@

Figure \ref{fig:habituals-predictive-figure} (left) shows the mean predicted future rate as a function of the past rate given to the participant and the type of causal information given. 
We observe in the baseline condition that future frequency perfectly tracks past frequency ($r(`r n.hab.pred.past.baseline.freq`) = `r format(r.hab.pred.past.baseline.freq, digits = 3)`$). 
That is, participants believe if a person smoked cigarettes 3 times last month, they will smoke cigarettes 3 times next month. 
This result implies that our model makes identical predictions for Expt. 2b whether the referent is past frequency or expected future frequency (indicating, as expected, that we must look to the new data to distinguish these models).
Critically, we observe the preventative information strongly decreases and the enabling information slightly increases predicted frequency (Figure \ref{fig:habituals-predictive-elicitation} left; blue and green dots).

```{r habituals-predictive-elicitation-predictions, eval=F}
lmer.rs.hab.predictive <- lmer(data = d.hab.predictive, 
     logAnnualPredictiveRate ~ logAnnualPastRate + condition + 
       (1 + condition | workerid) + 
       (1 + condition | item)
)
lmer.rs.hab.predictive.summary <- summary(lmer.rs.hab.predictive)
```

### 2018-02-08 paper/case3-causals.Rmd
port over more code into scripts

>>>>

```{r}
genericEndorsementPriorModelHelpers <- '
var eps = 0.01;//Number.EPSILON;
var log = function(x){ return Math.log(x) }
var exp = function(x){ return Math.exp(x) }

var avoidEndPoints = function(x){
  x == 0 ? eps : 
  x == 1 ? 1 - eps : 
  x
}

var preprocessedResponses = map(function(d){
  return avoidEndPoints(d / 100)
}, data)
'

structuredPriorModel <- '
var model = function(){
  var phi = uniformDrift({a:0, b: 1, width:0.2});
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  var transientComponent = Beta({a:1, b:100})
  mapData({data: preprocessedResponses}, function(d){
    factor( log(
      phi * exp(stableComponent.score(d)) +
      (1 - phi) * exp(transientComponent.score(d))
    ))
  })
  return {g, d, phi}
}
'

unstructuredPriorModel <- '
var model = function(){
  var g = uniformDrift({a:0, b: 1, width:0.2});
  var d = uniformDrift({a:0, b: 100, width:5});
  var stableParams = betaShape({g, d})
  var stableComponent = Beta(stableParams)
  mapData({data: preprocessedResponses}, function(d){
    factor(stableComponent.score(d))
  })
  return {g, d}
}
'
genericEndorsementPriorModel <- paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = "\n")
```

```{r rsaHelpers}
rsaHelpers <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var round = function(x){
  return Math.round(x*1000)/1000
}
var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
// var thetaBins = [
//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 // ]
var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var bins = map(round, _.range(0.01, 0.99, 0.01))

// var bins = [
  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
// ];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}

var mixture = data.prior.mix[0];
var priorParams = data.prior.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

fixed.threshold.model <- '
var fixedThresholdInterpreter = function(threshold) {
  Infer({model: function(){
  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
  var state = sample(statePrior)
  condition( state > threshold)
    return {
      state: state
  }
 // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
 }, method: "enumerate"})}
'

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

```{r simulationCalls}
fixed.threshold.calls <- '
_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
'
no.utterance.call <- ' 
  noUtteranceInterpreter()
'
uncertain.threshold.call <- '
  uncertainThresholdInterpreter()
'
```
